\documentclass[letter, 11pt]{moderncv}

% moderncv themes
\moderncvtheme[blue, sans]{classic}

% character encoding
\usepackage[utf8]{inputenc}
% adjust the page margins
\usepackage[scale=0.85]{geometry}
\recomputelengths{}

% personal data
\firstname{John}
\familyname{Whitaker}
\title{Software Engineer}
\address{2010D NW 60th St}{Seattle, WA 98107}
\mobile{(770) 833--3134}
\email{jake.whitaker@gmail.com}

\begin{document}
\maketitle

\section{Experience}

\cventry{2017 -- 2023}{Software Engineer II}{Google}{Cloud Storage Metering}{Seattle}{
  \begin{itemize}
		\item Rewrote storage usage metering job that calculates usage across all GCS customers from Java to C++, saving 90 percent in memory resource utilization.
		\item Led the development with a junior engineer for metering of dual region objects, a highly requested feature by current and potential customers. This required the changing of the core assumption that each bucket exists in a single region.
		\item Wrote a new metric implementation for a new custom contract being offered to one of our top 5 customers.
		\item Led a year long effort security improvement project to restructure and harden access controls for all of Cloud Storage.
		\item Helped eight new software engineers at a remote office onboard onto the team at once.
	\end{itemize}
}
\cventry{2016 -- 2017}{Software Engineer II}{Amazon}{Selection and Catalog Services}{Seattle}{
	\begin{itemize}
  \item Developed a migration plan to move a data processing system from a self hosted cluster to EMR to reduce developer and operational pain.
  \item Core contributor to an Amazon community project to simplify Elasticsearch usage and deployment within the company.
  \item Developed a long-term scaling and maintenance plan to support the Elasticsearch cluster.
	\end{itemize}
}
\cventry{2014 -- 2016}{Software Engineer I}{Amazon}{Selection and Catalog Services}{Seattle}{
	\begin{itemize}
  \item Collected requirements for a new internal data visualization application ensuring we met our users actual needs.
	\item Developed a document replication system that read from a bulk data output and wrote into Elasticsearch.
	\item Introduced the team to the Agile process and acted as team scrum master. 
	\item Developed an Elasticsearch storage schema model and service API to enable users to search and aggregate large amounts of data in realtime.
	\end{itemize}
}
\section{Languages}
\cvitem{\textbf{C++}}{Highly Proficient}{}
\cvitem{\textbf{Python}}{Highly Proficient}{}
\cvitem{\textbf{Java}}{Proficient}{}

\section{Developer Skills}
\cvlistitem{Distributed Systems}
\cvlistitem{DevOps}
\cvlistitem{Testing}
\cvlistitem{System design}

\section{Education}
\cventry{2014}{Bachelor of Arts, Computer Science with a Physics Minor}{University of Chicago}{\linebreak Chicago, IL}{}{}
\end{document}
