% LaTeX resume using res.cls
\documentclass[line,margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font

\begin{document}

\name{John S. Whitaker}
% \address used twice to have two lines of address
\address{3040 17th Ave W, Unit 508, Seattle, WA 98119}
\address{(770) 833-3134\\ jake.whitaker@gmail.com}

\begin{resume}
  
  \section{EXPERIENCE}

  {\sl Amazon.com, Inc}
  \hfill April 2016 -- Current
  Software Engineer II, Amazon Selection and Catalog Services, Seattle WA
  \begin{itemize}  \itemsep-2pt
  \item Member of company-wide community project to improve Elasticsearch usage and deployment within the company.
  \end{itemize}
  
  {\sl Amazon.com, Inc}
  \hfill July 2014 -- April 2016
  Software Engineer I, Amazon Selection and Catalog Services, Seattle WA
  \begin{itemize}  \itemsep-2pt
  \item Collected requirements for new internal application
  \item Developed the data storage layer and data transformation flows.  This utilizes DynamoDB for storage and SQS for the message queue.
  \item Moved the team to agile development and continue to lead team scrum.
  \item Designed and implemented a search cluster using Elasticsearch to support our UI requirements. 
  \item Released application to high user praise.
  \end{itemize}
  
  {\sl National Bureau of Economic Research}
  \hfill April 2011 -- August 2013 \\
  Research Professional, Economics Dept., University of Chicago, Chicago IL
  \begin{itemize}  \itemsep-2pt
  \item Created, edited, and proofread technical presentations and papers.
  \item Reviewed and edited galleys received from journals.
  \item Designed a new template streamlining the production of presentations and their associated notes.
  \item Produced documentation on the various tasks involved with the position.
  \end{itemize}
  
  {\sl University of Chicago Humanities Department}
  \hfill Summer 2010 \\
  Junior Web Developer, Humanities Computing Department,
  Chicago IL
  \begin{itemize}  \itemsep-2pt
  \item Maintained university websites running Drupal.
  \item Wrote a PHP script to update course webpages from an access database.
  \item Modified Drupal themes to the needs of each department.
  \end{itemize}

  
  {\sl FermiLab} \hfill Summer 2009 \\
  Undergraduate Researcher, CDF Detector, UChicago Group, Batavia IL
  \begin{itemize}  \itemsep-2pt
  \item Coded macros and small programs in ROOT, a system built on C++ used to analyze large data sets from the detector.
  \item Compared the distributions of data from monte carlo simulations and the detector to determine the origins of particle interactions.
  \end{itemize}
  
  \section{COMPUTER \\ SKILLS} {\sl Languages \& Software:}
  C++, C, FORTRAN, Scheme, HTML, CSS, Drupal, PHP, \LaTeX, MS Office or equivalent,
  Photoshop. \\
  {\sl Operating Systems:} Microsoft Windows
  (proficient), Linux (proficient), Macintosh (moderate).
  
  
  \section{EDUCATION} {\bf University of Chicago}, Chicago, IL \\
  Bachelor of Arts, Computer Science with a Physics Minor, 2014\\

  
  
\end{resume}
\end{document}







